\chapter{Testing and experimenting}

Detailed descriptions of every test case are definitely not what is required here. What is important is to show that you adopted a sensible strategy that was, in principle, capable of testing the system adequately even if you did not have the time to test the system fully.

Have you tested your system on ``real users''? For example, if your system is supposed to solve a problem for a business, then it would be appropriate to present your approach to involve the users in the testing process and to record the results that you obtained. Depending on the level of detail, it is likely that you would put any detailed results in an appendix.

The following sections indicate some areas you might include. Other sections may be more appropriate to your project. 

\section{Overall Approach to Testing and Experiments}

\section{Acceptance Testing}
A table was derived which broke down all of the stories into multiple different features. These features were then tested, and a comment was left if the test did not pass.

\begin{center} 
 \begin{tabular}{||c c c c||}  
 \hline
 Story & Feature Name & Pass/Fail & Comment \\
 \hline\hline
 Registration and Login & Register User Details &  Fail &  \begin{tabular}{@{}c@{}} Users postcode \\ does not get\\ added properly \end{tabular} \\
 \hline
 Registration and Login & \begin{tabular}{@{}c@{}}Login with \\ previously created \\ account \end{tabular} & Pass &  Works as expected \\
 \hline
 Registration and Login & Logout & Fail & \begin{tabular}{@{}c@{}} System appears to \\ logout okay however \\ it loads previous \\ users feed. \end{tabular} \\
 \hline
 Profile Page & \begin{tabular}{@{}c@{}} Upload picture \\ from library \end{tabular}  &  Pass  & Works as expected  \\ 
 \hline
Profile Page & \begin{tabular}{@{}c@{}}Take picture \\using device's camera \\ and upload.\end{tabular} & Pass &  Works as expected  \\ 
\hline
Profile Page & Update bio & Pass & Works as expected \\
\hline 
Post System & User Posts & Pass &  \begin{tabular}{@{}c@{}} User posts get \\ added to feed table \\ as expected. \end{tabular} \\
\hline
Follow System & \begin{tabular}{@{}c@{}} User can follow \\ other users \end{tabular} & Pass &  \begin{tabular}{@{}c@{}} adds data to \\ the correct table \\ and shows as followed \\ on the app \end{tabular} \\
\hline
Follow system &  \begin{tabular}{@{}c@{}} User can unfollow \\ other users \end{tabular} & Pass &  \begin{tabular}{@{}c@{}} Can successfully unfollow other users \end{tabular} \\
\hline
 \begin{tabular}{@{}c@{}} Post System \\ and Follow System \end{tabular} &  \begin{tabular}{@{}c@{}} Correct posts \\ display on users \\ home page \end{tabular} & Pass & The correct posts display \\
 \hline
 Create Events System & Create a Venue & Pass &  \begin{tabular}{@{}c@{}} All necessary details \\ are stored in the \\ back end appropriately \end{tabular} \\
\hline
 Create Events System & Create Events Themselves & Pass & \begin{tabular}{@{}c@{}} Events are \\ properly created \\ and have a correct \\ link to the appropriate \\ venue id. \end{tabular} \\
 \hline
 Search &  \begin{tabular}{@{}c@{}} User can search \\ for nearby events \end{tabular} & Pass &  \begin{tabular}{@{}c@{}} Uses device's GPS \\ correctly and compares \\ with events location \end{tabular} \\
 \hline
  Search &  \begin{tabular}{@{}c@{}} User can search \\ for nearby music \\ lovers and artists \end{tabular} & Pass &  \begin{tabular}{@{}c@{}} Uses device's GPS \\ correctly and compares \\ with events location \end{tabular} \\
  \hline
   Search &  \begin{tabular}{@{}c@{}} User can search \\ for events \\ which are happening \\ soon \end{tabular} & Pass &  \begin{tabular}{@{}c@{}} Correctly sorts \\ events by dates  \end{tabular} \\
  \hline
\end{tabular}
\end{center}
 \captionof{table}{User Acceptance Testing Table}
\vspace{5mm}

It is clear from Table 4.1 that in terms of acceptance testing some of the code contained bugs for example the logout system was not working properly. Once all of the issues in Table X had been addressed another table; Table Y was created, this goes through the tests which failed in Table X and evaluates whether they now pass.

\section{Unit tests}
It is important to unit test each of the functions within the controllers to make sure that the user of the app wont encounter any weird behaviour. The Jasmine and Karma frameworks were used for unit testing the app.  

\section{User Interface testing}
For a mobile app user interface testing is very important. As the user interface is essentially how the user natvigates around the front end and how they submit data to the back end. 

\section{}

\section{User testing}
In establishing whether hybrid apps are feasible alternatives to native apps it was important to get general users say about whether the apps 